Network Configuration Synthesis with Abstract Topologies

### 2016-11-07 paper/abstraction/paper.tex
edits to intro and sec 3

An important class of networks are the large \emph{structured networks}
commonly deployed in industrial data centers.  These networks run
many critical services and every second of downtime is at best
costly and at worst dangerous.  Unfortunately, it is an enormous
challenge to keep these complex networks up and
running 24/7~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
Moreover, while hardware faults, rodents, power failures and natural
disasters can all cause significant downtime, studies have shown that
\emph{human error}, which occurs during network configuration or
update, is the single large cause of these
outages~\cite{juniper-study}.

@@

Unfortunately, such templates have no particular semantics other than the
semantics
that one obtains from instantiating a template's parameters.
\dpw{add blah blah about low-level, assembly language, device by device}
Moreover,
template construction is a manual process:  network engineers do their
best to design templates that will work effectively in the context
of their particular network topology.  However, there is no support for
validating key properties of an assembly of templates, such as connectivity
and fault tolerance,
aside from instantiating the templates and testing.  In addition,
network engineers have no tools to help them design for network
evolution.  For instance, the process of adding new equipment to
expand the capacity of data center may not be compatible with the original
templates, or may cause a trickle-down of changes to be made network-wide.
Each change to a router configuration typically incurs
some risk of temporary instable in a network, so minimizing such changes
is an important design goal.  It is no wonder that a major
network outage, such as the one that grounded all United Air flights
in July 2015~\cite{x}, makes international news every few months.

@@

During compilation, the \sysname compiler also analyzes policy with respect to the
abstract topology and guarantees that the configurations will
faithfully implement the high-level policy on \emph{any} concrete
topology that satisfies the given connectivity invariants.  The compiler
will also optionally perform a second fault tolerance analysis that
determines the minimum number of link failures required to disconnect
\emph{any} concrete topology that once again satisfies the connectivity
invariants.

@@

\begin{enumerate}
\item Design of new topology abstractions involving roles and
connectivity invariants for network programmers.
\item Design of two new algorithms for analyzing routing policy over
abstract networks: one which
guarantees correct compilation and one which determines fault tolerance
properties of network policy.  Both algorithms provide guarantees for any
concrete network satisfying the abstract connectivity invariants.
\item Design of template generation algorithms that support network
evolution.
\item Implementation and evaluation of a \sysname compiler that generates
configuration templates and is up to two orders of magnitude faster
than its closest competitor on large networks.
\end{enumerate}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example3}
  \caption{Role-based abstraction for the datacenters in Figure~\ref{fig:example}.}
  \label{fig:example3}
  \vspace{-1em}
\end{figure}

>>>>

An important class of networks are the large \emph{structured networks}
commonly deployed in industrial data centers.  These networks run
many critical services; every second of downtime is
costly at best and dangerous at worst.  Unfortunately, it is an enormous
challenge to keep these complex networks up and
running 24/7~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
Moreover, while hardware faults, rodents, power failures and natural
disasters can all cause significant downtime, studies have shown that
\emph{human error}, which occurs during network configuration or
update, is the single largest cause of these
outages~\cite{juniper-study}.

@@

Unfortunately, such templates have no particular semantics other than the
semantics
that one obtains from instantiating a template's parameters.
Moreover,
template construction is a low-level, manual process:  
network engineers do their
best to design templates using assembly-language-like primitives.
They hope their templates
that will work properly, test them using simulations, but
there is no support for verification of key network-wide properties 
such as connectivity and fault tolerance. In addition,
network engineers have no tools to help them design for network
evolution.  For instance, the process of adding new equipment to
expand the capacity of data center may not be compatible with the original
templates, or may cause a trickle-down of changes to be made network-wide.
Each change to a router configuration typically incurs
some risk of temporary instable in a network, so minimizing such changes
is an important design goal.  
%It is no wonder that a major
%network outage, such as the one that grounded all United Air flights
%in July 2015~\cite{x}, makes international news every few months.

@@

During compilation, the \sysname compiler also analyzes policy with respect to the
abstract topology and guarantees that the configurations will
faithfully implement the high-level policy on \emph{any} concrete
topology that satisfies the given connectivity invariants.  The compiler
will also optionally perform a second fault tolerance analysis that
determines the minimum number of link failures required to disconnect
\emph{any} valid concrete topology.

@@

\begin{enumerate}
\item Design of new topology abstractions for network programming
based on graph homomorphisms and connectivity invariants.
\item Design of two new algorithms for analyzing routing policy over
abstract networks: one which
guarantees correct compilation and one which determines fault tolerance
properties of network policy.  Both algorithms provide guarantees for any
concrete network satisfying the abstract connectivity invariants.
\item Design of template generation algorithms that support network
evolution.
\item Implementation and evaluation of a \sysname compiler that generates
configuration templates and is up to two orders of magnitude faster
than its closest competitor on large networks.
\end{enumerate}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example3}
  \caption{An abstraction for the datacenters in Figure~\ref{fig:example}.}
  \label{fig:example3}
  \vspace{-1em}
\end{figure}
